---
title: "work shop 7- assignment test 3"
author: "Mariam s4664140"
date: "25/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(skimr)
```

### Data set exploration and identifying a business problem(= main question to solve)
```{r}
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')

```
**questions**:how can i predict of rating of coffee?(=which means what factors affects its rating= quality )
**sub question **:
does altitude affect quality?
does the place of origin affect its rating(country,owner, farm)
are all robusta beans rated low?
what are most acidic coffee beans ?
lets look at data 
```{r}
skim(coffee_ratings)
```
lets look at the rating boxplot

```{r}
coffee_ratings%>%ggplot(
  aes(total_cup_points)
)+
  geom_boxplot()

coffee_rating_clean<-coffee_ratings%>%filter(total_cup_points>69)
coffee_ratings%>%ggplot(aes(aroma)
                        )+
  geom_boxplot()
```
doing another varible with the box plot 



lest explore factors !
```{r}
coffee_ratings%>%count(species,sort=TRUE)
coffee_ratings%>%count(variety,sort = TRUE)
```
'variety' should be factor!

get rid of NA (removing using filters)
```{r}
coffee_rating_clean<-coffee_ratings%>%
  mutate(variety=as_factor(variety))%>%
  filter(!is.na(variety))
coffee_rating_clean<-coffee_rating_clean%>%
  mutate(
    variety=fct_lump_n(coffee_rating_clean$variety, n=4)
    )

coffee_rating_clean%>%
  count(variety, sort=TRUE)

```

can i lump up variety categories with low number of observations


lets explore relation between altitude mean meter and total cup of points 

```{r}
coffee_rating_clean%>%ggplot(
  aes(x=altitude_mean_meters,y=total_cup_points)
)+
  geom_point()


coffee_rating_clean%>%ggplot(
  aes(x=altitude_mean_meters,y=total_cup_points)
)+
  
  geom_smooth(method = lm)

```
linar model(predicting total cup points based on altitude mean meters and save it to the variable res)
```{r}
library(tidyverse)
library(broom)
res<-lm(total_cup_points~altitude_mean_meters+number_of_bags+acidity, data=coffee_rating_clean)

summary(res)
```
ASSIGNMENT 
